---
title: "Alcohol vs Seat choice"
author: "Jonathan Campos"
date: "Summer 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  Based off the box plot the median of people who sit in the back as I see it is higher than both the third quartile of people who sit in the front and the third quartile those who sit in the middle.
### get fancy  

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

The third quantile od the front is 2 and the third quantile of the middle is 3. The median of the back is 4 so in this case the median of the back is higher than the third auantile of both the front and middle.

## Inferential Tests


```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

After running the inferential test we find hat the probability of the people in the front and middle consuming the same amount of alcohol as the people in the back being 0.000116. Therefore there is a significant difference between 3.

```{r}
plot(TukeyHSD(model1))
```

When looking at the model we see that the middle compared to the back does not have 0 in their confidence interval. The same is true when you compare the front and back. This also indicated that their is not statistical difference between the front and the middle. The back is different from everbody else. 

## Conclusions

When going through the process with more than two variables there are more steps that we have to go through which can complicate the process. In this assignmetn we used ggplot to create our boxplot which showed us the median of how much alcohol was consumed per section. Then we ran a numerical summary of the information so that we could get exact numbers and see how big the difference was. Then we want the inferential test to get the probability of these three sections cinsuming the same amount of alchohol which was 0.000116. After this we used a compatison model that showed us how significant the difference between each section was. I have came to the conclusion that there is a significant difference bwtween how mcuh alcohol the three sections consumed.

