---
title: "Alcohol vs Seat choice"
author: "Jonathan Campos"
date: "Summer 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  Based off the box plot the median of people who sit in the back as I see it is higher than both the third quartile of people who sit in the front and the third quartile those who sit in the middle.
### get fancy  

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

The third quantile od the front is 2 and the third quantile of the middle is 3. The median of the back is 4 so in this case the median of the back is higher than the third auantile of both the front and middle.

## Inferential Tests


```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

After running the inferential test we find hat the probability of the people in the front and middle consuming the same amount of alchool as the people in the back being 0.000116. Therefore there is a significant difference between 3.

## Conclusions


